Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-20 paper/main.tex
delete extra space
cleaned up new figures, added new fig 7, recompiled pdf with new versions

We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
responses to a small set of multiple-choice questions to estimate how much the
participant ``knows'' about the concept reflected by any arbitrary coordinate,
$x$, in text embedding space (e.g., the content reflected by any moment in a
lecture they had watched; see \nameref{subsec:traces}). Essentially, the
estimated knowledge at coordinate $x$ is given by the weighted average
proportion of quiz questions the participant answered correctly, where the
weights reflect how much each question is ``about'' the content at $x$. When we
apply this approach to estimate the participant's knowledge about the content
presented in each moment of each lecture, we can obtain a detailed timecourse
describing how much ``knowledge'' the participant has about any part of the
lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
this approach to the questions from each quiz taken throughout the experiment, separately.

From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
high-resolution snapshot (at the time each quiz was taken) of what the
participants knew about any moment's content, from either of the two lectures
they watched (comprising a total of 1,100 samples across the two lectures).

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/held-out-question-analysis}

@@

>>>>

We developed a simple formula (Eqn.~\ref{eqn:prop}) for using a participant's
responses to a small set of multiple-choice questions to estimate how much the
participant ``knows'' about the concept reflected by any arbitrary coordinate,
$x$, in text embedding space (e.g., the content reflected by any moment in a
lecture they had watched; see \nameref{subsec:traces}). Essentially, the
estimated knowledge at coordinate $x$ is given by the weighted average
proportion of quiz questions the participant answered correctly, where the
weights reflect how much each question is ``about'' the content at $x$. When we
apply this approach to estimate the participant's knowledge about the content
presented in each moment of each lecture, we can obtain a detailed timecourse
describing how much ``knowledge'' the participant has about any part of the
lecture. As shown in Figure~\ref{fig:knowledge-timeseries}A and C, we can apply
this approach separately for the questions from each quiz participants took
throughout the experiment. From just a few questions per quiz (see~\nameref{subsec:traces}), we obtain a
high-resolution snapshot (at the time each quiz was taken) of what the
participants knew about any moment's content, from either of the two lectures
they watched (comprising a total of 1,100 samples across the two lectures).

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=0.7\textwidth]{figs/predict-knowledge-questions}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/knowledge-smoothness}

    \caption{\textbf{Caption title.} Caption content.}

    \label{fig:smoothness}
\end{figure}
